%  pdflatex slides

\documentclass[landscape]{slides}
\usepackage{url}
\pagestyle{empty}
\hoffset 1in
\begin{document}
\begin{slide}
 \begin{center}
  {\bf\Large F90 Testkit}\\
  \vspace{0.5in}
  \begin{minipage}{6.5in}
    {\bf Goal:} to make Fortran~90 unit/\-mobility/\-developer testing
    as painless as possible.
  \end{minipage}
 \end{center}
\end{slide}
\begin{slide}
  \begin{center}
    {\bf\Large Why write tests?}\\
    \vspace{0.5in}
    \begin{minipage}[t]{3in}
     \begin{itemize}
      \item Shame
      \item Embarrassment
      \item Speed
      \item Confidence
     \end{itemize}
    \end{minipage}
    \begin{minipage}[t]{3in}
     \begin{itemize}
      \item Trust
      \item Change
      \item Documentation
     \end{itemize}
    \end{minipage}
  \end{center}
\end{slide}
\begin{slide}
  \begin{center}
    {\bf\Large Why write tests first?}\\
    \vspace{0.5in}
    \begin{minipage}{3in}
    \begin{itemize}
     \item Tests get written
     \item Succinctness
     \item Clarity
     \item Closure
    \end{itemize}
    \end{minipage}\\
    \vspace{1in}
    \begin{minipage}{5.7in}\raggedright
      ``No code should be written or changed unless there is a failing
      test.''
    \end{minipage}
  \end{center}
\end{slide}
\begin{slide}
  \begin{center}
   {\bf\Large How do I add tests to legacy code?}\\
   \vspace{0.5in}
   \begin{minipage}{6in}
    \begin{itemize}
     \item Fixing Bugs
      \begin{itemize}
       \item write test for bug {\small (which fails)}
       \item write code to satisfy failing test
       \item write tests/code for similar cases
      \end{itemize}
      \vspace{8pt}
     \item Adding Features
      \begin{itemize}
       \item write test for feature {\small (which better fail)}
       \item write code to satisfy failing test
      \end{itemize}
      \vspace{8pt}
     \item Refactoring ``Bad Smells''
      \begin{itemize}
       \item write tests to cover existing code
       \item update/add tests for new structure
       \item change code to satisfy failing tests
      \end{itemize}
    \end{itemize}
   \end{minipage}
  \end{center}
\end{slide}
\begin{slide}
  \begin{center}
    {\bf\Large Crazy enough to learn more?}\\
    \vspace{0.5in}
    \begin{minipage}{6in}
     \begin{itemize}
      \item \url{http://c2.com/cgi/wiki?UnitTests}\\[-10pt]
      \item \url{http://xprogramming.com/software.htm}
     \end{itemize}
    \end{minipage}
  \end{center}
\end{slide}
\begin{slide}
  \begin{center}
    {\bf\Large Want to try F90 testkit?}\\
    \vspace{0.5in}
    \begin{minipage}{9in}
     \begin{itemize}
      \item Have your SA install Ruby {\small(or install it yourself)}\\[5pt]
       \hspace*{1em}\url{http://www.ruby-lang.org/}\\[5pt]
      \item Check out the FTK repository\\[5pt]
       \hspace*{1em}\verb+cvs -d :pserver:[username]@abnode3:/usr/local/cvsroot \+\\
       \hspace*{1em}\verb+checkout -P FTK+\\[5pt]
       where \verb+[username]+ is your CVS username on \verb+abnode3+
     \end{itemize}
    \end{minipage}
  \end{center}
\end{slide}
\begin{slide}
  \begin{center}
    {\bf\Large Who does what?}\\
    \vspace{0.5in}
    {\bf You:}
    \begin{minipage}[t]{6.5in}\raggedright
     \begin{enumerate}
      \item Create testsuite file, e.g., \verb+RoutineTS.ftk+
      \item Write test in Fortran with embedded assert macros, .e.g,
        \verb+IsTrue(x>2)+
      \item Run testsuite {\small (it should fail)}
      \item Write \verb+Routine.f90+ to satisfy test
     \end{enumerate}
     \vspace{10pt}
     Repeat steps 2, 3, and 4 until your objective is met.
    \end{minipage}\\
    \vspace{0.8in}
   {\bf It:}
   \begin{minipage}[t]{6in}\raggedright
   Translates, compiles, links, and runs tests.
   \end{minipage}
  \end{center}
\end{slide}
\end{document}
